Report

### 2021-07-27 Rmd/report_04_gca_relaxed.Rmd
Add 25 months analysis

```{r gaze_time_vocab_lower_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

>>>>

```{r gaze_time_vocab_lower_relaxed, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper_relaxed, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

### 2021-07-27 Rmd/report_04_gca_stringent.Rmd
Add 25 months analysis

```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

>>>>

```{r gaze_time_vocab_lower, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	count(age_group, lp)

@@

```{r gaze_time_vocab_upper, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

### 2021-07-27 Rmd/report_08_mon_stringent.Rmd
Add 25 months analysis

```{r define_model_mon_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_mon <- model_fits_relaxed$fit_mon
```

```{r fixef_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_mon, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_mon, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

@@

```{r gaze_time_mon_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- augment(fit_mon) %>%
	distinct(participant, age_group) %>% 
	count(age_group)

>>>>

```{r define_model_mon_stringent, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_mon <- model_fits$fit_mon
```

```{r fixef_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_mon, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_mon, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

@@

```{r gaze_time_mon_stringent, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- augment(fit_mon) %>%
	distinct(participant, age_group) %>% 
	count(age_group)
